Manuscript Figures for Genome Biology

### 2018-07-25 manuscript_figures/manuscript_figures.Rmd
Add informative covariate impact line plot; remove unnecessary figs

# not excluding any methods
Fig4All.rowOrder <- c("bonf", "bh", "ihw", "qvalue", "bl", "lfdr",
                  "fdrreg-e", "fdrreg-t", "ashq")
Fig4All <- plotMethodRanks(objects, colLabels = casestudy, alpha = alpha,
                        excludeMethods = NULL, rowOrder = Fig4All.rowOrder) +
        theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1),
              legend.position = c(0.96, 0.93), legend.justification = c(1, 1),
              legend.background = element_rect(fill = scales::alpha("white", 3/4), color = 'black'),
              legend.direction = "horizontal",
              legend.text = element_text(size = 7),
              legend.title = element_text(size = 9),
              legend.margin = margin(6, 10, 6, 10))

@@

xtable(tabS3)

@@

pfdr <- plotMethodRanks(objs, 
                colLabels = c("sim", "sim"), 
                alpha = alpha, xlab = "Comparison",
                fill = "FDR",
                rowOrder = Fig4All.rowOrder, 
                annotate = "FDR", excludeMethods = NULL) +
          scale_fill_gradient2(high = "darkred", 
                         mid = "white", 
                         low = "darkblue", 
                         midpoint = alpha) +
          labs(fill = "Mean FDR") +
          theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1),
              legend.justification = c(1, 0.5),
              legend.text = element_text(size = 7),
              legend.title = element_text(size = 8),
              legend.margin = margin(1, 1, 1, 1)) +
          ylab("") + xlab("") +  
          theme(plot.margin=unit(c(5.5, 5.5, 30, 5.5), "points"))

@@

ggdraw() +
  draw_plot(pfdr, 0.51, 0, 0.24, 1) +
  draw_plot(ptpr, 0.75, 0, 0.24, 1) +
  draw_plot(Fig4All, 0, 0, 0.5, 1) +
  draw_plot_label(c("A", "B"), c(0, 0.51), c(1, 1), size = 15) +
  draw_plot_label("Simulation", 0.72, 0.06, size =11, fontface = "plain")
ggsave(file.path(outdir, "Figure4.pdf"), width=11, height=5)

@@

```{r, fig.width = 6, fig.height = 4}
library(ggbeeswarm)

casestudy.tab <- mutate(casestudy.tab, prop_casestudy = mean_prop) %>%
  select(casestudy, method, prop_casestudy)
yeastsim.tab <- yeastsim.tab %>% 
  mutate(prop_yeastsim = mean_prop) %>% 
  filter(casestudy == "de5") %>%
  select(casestudy, method, prop_yeastsim)

@@

ggplot(rank.tab , 
       aes(y = prop_casestudy, x = method, group = method, fill = Method)) +
  geom_boxplot(alpha=0.7) +
  scale_fill_manual(values=col) +
  theme_bw() +
  xlab("Method (ordered by rejections in yeast simulation (n=5))") +  
  ylab("Proportion of maximum rejections in casestudies")
ggsave(file.path(outdir, "Figure_simVcasestudyRanks.pdf"), width=6, height=4)

ggplot(rank.tab , 
       aes(y = prop_casestudy, x = method, group = method, color = Method)) +
  geom_boxplot(aes(x = prop_yeastsim, group = as.factor(prop_yeastsim), y = prop_casestudy),
                   alpha = 0.3, width = 0.04, outlier.shape = NA) +
  scale_color_manual(values=col) +
  theme_bw() +
  xlab("Proportion of maximum rejections in yeast simulation (n=5)") +  
  ylab("Proportion of maximum rejections in casestudies") +
  labs(shape = "Case Study") 
ggsave(file.path(outdir, "Figure_simVcasestudyRanks_points.pdf"), width=6, height=4)

@@

## Case-study specific plot analagous to Figure 2

Figure 2 panels C-E for a case study. For now picking GWAS.

```{r Figure2.5,  fig.width = 10, fig.height = 4}
objects <- list.files( path, recursive=TRUE, pattern="rds", full.names=TRUE )
resfile <- objects[grepl("GWAS", objects) & grepl("maf", objects)] 
res <- readRDS(file=resfile)
assayNames(res) <- "qvalue"
res <- addDefaultMetrics(res)

# Figure 2C: Total number of discoveries varied across method
p3 <- rejections_scatter(res, supplementary = FALSE) +
      theme(legend.position="none")+ 
  ggtitle("Number of rejections by alpha cutoff") + 
  xlab("alpha cutoff") +
  theme(axis.title = element_text(face="bold", size = 10),
        plot.title = element_text(face="bold", size = 14))

# Figure 2D: Some methods are tailored to detecting smaller effect sizes
p4 <- covariateLinePlot(res, alpha=alpha, covname="effect_size", trans="log1p",
                        transx = "exp", nbins=25)
leg <- get_legend(p4)
p4 <- p4 + theme(legend.position="none") + 
  ggtitle("Mean % significant by effect size %ile") + 
  theme(axis.title = element_text(face="bold", size = 10),
        plot.title = element_text(face="bold", size = 14)) +
  xlab("Effect size percentile")

# Figure 2E - upsetr plot - save separately
pdf(file.path(outdir, "FigureS0C.pdf"), width = 10, height = 4, onefile=FALSE)
plotFDRMethodsOverlap(res, 
                      alpha=alpha, nsets=ncol(res),
                      order.by="freq", decreasing=TRUE,
                      supplementary=FALSE, nintersects = 18) 
grid.text("Overlap for GWAS Case study, MAF covariate", x = 0.6, y = 0.97, 
          gp = gpar(fontsize = 16, fontface = "bold"))
grid.text("C", x = 0.02, y = 0.97, 
          gp = gpar(fontsize = 24, fontface = "bold")) 
dev.off()

# Figure 2 (ALL)
Fig2 <- plot_grid(p3, p4, ncol = 2, 
          labels = LETTERS[1:2], label_size = 20)
Fig2 <- plot_grid(Fig2, leg, ncol = 2, rel_widths = c(1, 0.2))
Fig2
ggsave(file.path(outdir, "FigureS0A-B.pdf"), width=10, height=4)

@@

Here we'll contrast the results of informative and uninformative covariates 
on the yeast simulation (null and DE sample size 5).

```{r FigureS7,  fig.width = 10, fig.height = 7}
objects <- list.files( path, recursive=TRUE, pattern="rds", full.names=TRUE )
resfile <- objects[grepl("yeast", objects) & 
                   grepl("de5|null5", objects)] 
de5 <- readRDS(file=resfile[grepl("de5", resfile) & !grepl("uninf", resfile)])
de5_uninf <- readRDS(file=resfile[grepl("de5", resfile) & grepl("uninf", resfile)])
null5 <- readRDS(file=resfile[grepl("null5", resfile) & !grepl("uninf", resfile)])
null5_uninf <- readRDS(file=resfile[grepl("null5", resfile) & grepl("uninf", resfile)])
excludeSet <- c("unadjusted", "bl-df02", "bl-df04", "bl-df05")

res5d <- plotsim_standardize(de5, alpha = seq(0.01, 0.10, 0.01))
res5d_u <- plotsim_standardize(de5_uninf, alpha = seq(0.01, 0.10, 0.01))
res5n <- plotsim_standardize(null5, alpha = seq(0.01, 0.10, 0.01))
res5n_u <- plotsim_standardize(null5_uninf, alpha = seq(0.01, 0.10, 0.01))

pa <- plotsim_average(res5n_u, met="TNR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) +
        expand_limits(y=0.93) +
        xlab("") +
        ggtitle("")

pb <- plotsim_average(res5n, met="TNR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) +
        theme(legend.position="none", plot.title = element_text(hjust = 0.5))+
        expand_limits(y=.93) +
        xlab("") +
        ggtitle("")

pc <- plotsim_average(res5d_u, met="FDR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) +
        theme(legend.position="none") +
        expand_limits(y=0.18) +
        xlab("") +
        ggtitle("")

pd <- plotsim_average(res5d, met="FDR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) +
        theme(legend.position="none") +
        expand_limits(y=0.18) +
        xlab("") +
        ggtitle("")

pe <- plotsim_average(res5d_u, met="TPR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) +
        theme(legend.position="none") +
        expand_limits(y=c(0.10,0.55)) +
        ggtitle("")

pf <- plotsim_average(res5d, met="TPR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) +
        theme(legend.position="none") +
        expand_limits(y=c(0.10,0.55)) +
        ggtitle("")

leg <- get_legend(pa)
pa <- pa + theme(legend.position="none", plot.title = element_text(hjust = 0.5))

FigT  <- plot_grid(pa, pb, ncol = 2, 
          #labels = LETTERS[1:2], 
          label_size = 20)

FigB  <- plot_grid(pc, pd, pe, pf, ncol = 2, 
          #labels = LETTERS[3:6], 
          label_size = 20)

Fig <- ggdraw() +
  draw_plot(FigT + ylab("") + xlab(""), 0, 0.64, 1, 0.3) +
  draw_plot(FigB + ylab("") + xlab(""), 0.005, 0, 1, 0.6) +
  draw_plot_label(c("Uninformative Covariate", "Informative Covariate"), 
                  c(0.14, 0.64), c(1,1), c(0,0), size = 15) +
  draw_plot_label(c("Null Simulation", "DE Simulation"), 
                  c(0.36, 0.37), c(0.96,0.62), size = 13)

Fig <- plot_grid(Fig, leg, ncol = 2, rel_widths = c(1, 0.2))
Fig
ggsave(file.path(outdir, "FigureS7.pdf"), width=10, height=11)

## Within case-study heatmaps of method rankings

Here we generate heatmaps for each case study, where each column represents a different
dataset. Here we pick one representative covariate and method (if applicable) 
for each case study. See the individual Rmds for more detailed plots comparing, e.g.
different covariates on the same dataset.

```{r}
objects <- list.files( path, recursive=TRUE, pattern="rds", full.names=TRUE )

# grab casestudy names
obj.names <- str_split(objects, pattern = "/")
casestudy <- unlist(lapply(obj.names, function(x) x[3] ))
dataset <- unlist(lapply(obj.names, function(x) x[4] ))
```

### GWAS

```{r, fig.width = 5, fig.height = 4.5}
# by covariate
wcs <- which(grepl("GWAS", casestudy))
objs <- objects[wcs]
labs <- unlist(lapply(str_split(dataset[wcs], pattern = "-"), 
                      function(x) x[2]))
plotMethodRanks(objs, colLabels = labs, alpha = alpha, xlab = "Covariate",
                excludeMethods = NULL, Nlabel = FALSE, annotate = "propPossible") + 
  ggtitle("GWAS") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1))
ggsave(file.path(outdir, "FigureS1.pdf"), width=5, height=4.5)
```

### GSEA

```{r,  fig.width = 6, fig.height = 4.5}
#by dataset
wcs <- which(grepl("GSEA", casestudy))
objs <- objects[wcs]
labs <- unlist(lapply(str_split(dataset[wcs], pattern = "-benchmark.rds"), 
                      function(x) x[1]))
plotMethodRanks(objs, colLabels = labs, alpha = alpha, xlab = "Dataset", 
                Nlabel = FALSE, annotate = "propPossible") + 
  ggtitle("GSEA") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1))
ggsave(file.path(outdir, "FigureS2.pdf"), width=6, height=4.5)
```

### ChIP-seq

```{r, fig.width = 5, fig.height = 5}
wcs <- which(grepl("ChIPseq", casestudy))
objs <- objects[wcs]
labs <- unlist(lapply(str_split(dataset[wcs], pattern = "-benchmark.rds"), 
                      function(x) x[1]))
plotMethodRanks(objs, colLabels = labs, alpha = alpha, xlab = "Dataset", 
                Nlabel = FALSE, annotate = "propPossible") + 
  ggtitle("ChIP-Seq") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1))
ggsave(file.path(outdir, "FigureS3.pdf"), width=5, height=5)
```

### RNA-seq
```{r, fig.width = 6, fig.height = 5}
# by dataset
wcs <- which(grepl("RNAseq", casestudy) & 
            !grepl(c("polyester|yeast"), objects) &
            !grepl("scRNAseq", casestudy))
objs <- objects[wcs]
labs <- unlist(lapply(str_split(dataset[wcs], pattern = "-benchmark.rds"), 
                      function(x) x[1]))
plotMethodRanks(objs, colLabels = labs, alpha = alpha, xlab = "Dataset", 
                excludeMethods = NULL, Nlabel = FALSE, annotate = "propPossible") + 
  ggtitle("RNA-seq") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1))
ggsave(file.path(outdir, "FigureS4.pdf"), width=6, height=5)
```

### scRNA-seq

```{r, fig.width = 15, fig.height = 6}
wcs <- which(grepl("scRNAseq", casestudy))
objs <- objects[wcs]
ds <- unlist(lapply(str_split(dataset[wcs], pattern = "-benchmark-"), 
                      function(x) x[1]))
m0 <- unlist(lapply(str_split(dataset[wcs], pattern = "-benchmark-"), 
                      function(x) x[2]))
meth <- unlist(lapply(str_split(m0, pattern = "-"), 
                      function(x) x[1]))
cv <- gsub(".rds", "", unlist(lapply(str_split(m0, pattern = "-"), 
                      function(x) x[2])))

uninf <- which(grepl("uninf", objs))

# by dataset
pa <- plotMethodRanks(objs[-uninf], colLabels = ds[-uninf], alpha = alpha, 
                      xlab = "Dataset", annotate = "propPossible") + 
  ggtitle("scRNA-seq")+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1))

# by method
pb <- plotMethodRanks(objs[-uninf], colLabels = meth[-uninf], alpha = alpha,
                      xlab = "Method", annotate = "propPossible") + 
  ggtitle("scRNA-seq")+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1))

# by covariate
pc <- plotMethodRanks(objs, colLabels = cv, alpha = alpha,
                      xlab = "Covariate", annotate = "propPossible") + 
  ggtitle("scRNA-seq")+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1))

plot_grid(pa, pb, pc, ncol=3)
ggsave(file.path(outdir, "FigureS5.pdf"), width=15, height=6)
```

### Microbiome

```{r, fig.width = 14, fig.height = 6.5}
# by dataset, excluding otu when genus is available
# excluding log-ubiquity
# excluding enigma-so4 (no discoveries)
wcs <- which(grepl("microbiome", casestudy) & 
              !(grepl(c("goodrich|papa"), dataset) & 
              grepl(c("otu"), dataset)) &
              !grepl("log-ubiquity", dataset) &
              !grepl("so4", dataset) &
              !grepl("baxter", dataset) )
objs <- objects[wcs]
labs <- unlist(lapply(str_split(dataset[wcs], pattern = "-benchmark.rds"), 
                      function(x) x[1]))
plotMethodRanks(objs, colLabels = labs, alpha = alpha, xlab = "Dataset", 
                Nlabel = FALSE, annotate = "propPossible") + 
  ggtitle("Microbiome")+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1))
ggsave(file.path(outdir, "FigureS6.pdf"), width=14, height=6.5)
```

### Yeast Simulation

```{r}
# non-null
wcs <- which(grepl("RNAseq", casestudy) & 
            !grepl(c("brain|mir|polyester|null"), objects) &
            !grepl("scRNAseq", casestudy))
objs <- objects[wcs]
labs <- gsub(".rds", "", 
             unlist(lapply(str_split(dataset[wcs], pattern = "-results-"), 
                      function(x) x[2])))

plotMethodRanks(objs, 
                colLabels = labs, 
                alpha = alpha, xlab = "Comparison",
                excludeMethods = NULL,
                annotate = "propPossible")

plotMethodRanks(objs, 
                colLabels = labs, 
                alpha = alpha, xlab = "Comparison",
                excludeMethods = NULL, 
                fill = "FDR",
                annotate = "propPossible")

plotMethodRanks(objs, 
                colLabels = labs, 
                alpha = alpha, xlab = "Comparison",
                excludeMethods = NULL, 
                fill = "TPR",
                annotate = "propPossible")

# null
wcs <- which(grepl("RNAseq", casestudy) & 
            !grepl(c("brain|mir|polyester|de"), objects) &
            !grepl("scRNAseq", casestudy))
objs <- objects[wcs]
labs <- gsub(".rds", "", 
             unlist(lapply(str_split(dataset[wcs], pattern = "-results-"), 
                      function(x) x[2])))

plotMethodRanks(objs, 
                colLabels = labs, 
                alpha = alpha, xlab = "Comparison",
                excludeMethods = NULL,
                annotate = "propPossible")

### Polyester Simulation

```{r}
wcs <- which(grepl("RNAseq", casestudy) & 
            !grepl(c("brain|mir|yeast|null"), objects) &
            !grepl("scRNAseq", casestudy))
objs <- objects[wcs]
labs <- gsub(".rds", "", 
             unlist(lapply(str_split(dataset[wcs], pattern = "-results-"), 
                      function(x) x[2])))

plotMethodRanks(objs, 
                colLabels = labs, 
                alpha = alpha, xlab = "Comparison",
                excludeMethods = NULL)

plotMethodRanks(objs, 
                colLabels = labs, 
                alpha = alpha, xlab = "Comparison",
                excludeMethods = NULL, 
                fill = "FDR")

plotMethodRanks(objs, 
                colLabels = labs, 
                alpha = alpha, xlab = "Comparison",
                excludeMethods = NULL, 
                fill = "TPR")

# null
wcs <- which(grepl("RNAseq", casestudy) & 
            !grepl(c("brain|mir|yeast|de"), objects) &
            !grepl("scRNAseq", casestudy))
objs <- objects[wcs]
labs <- gsub(".rds", "", 
             unlist(lapply(str_split(dataset[wcs], pattern = "-results-"), 
                      function(x) x[2])))

plotMethodRanks(objs, 
                colLabels = labs, 
                alpha = alpha, xlab = "Comparison",
                excludeMethods = NULL) 
```

# Alternative Supplementary Figures

## All Case Studies

This plot is an alternative to Supplementary Figures S1-S6.
We include all case studies in a single plot.

@@

# Informativeness of covariates in case studies

@@

# Informativeness of covariates in Yeast & Polyester simulation

As an alternative to the line plot above (Figure S7), we make a heatmap plot that
displays the mean difference within simulation replicate.

```{r}

for (org in c("yeast", "polyester")){

objects <- list.files( path, recursive=TRUE, pattern="rds", full.names=TRUE )
resfile <- objects[grepl(org, objects) ]

# regexp to construct master data table separating case study datasets, methods
# and covariates
obj.names <- str_split(resfile, pattern = "/")
casestudy <- unlist(lapply(obj.names, function(x) x[3] ))
filename <- gsub(".rds", "", unlist(lapply(obj.names, function(x) x[4] )))
dataset <- unlist(lapply(str_split(filename, pattern = "-"), function(x) x[[3]]))
inform <-  ifelse(grepl("uninf", resfile), "uninf", "inf")
type <-  ifelse(grepl("null", resfile), "null", "de")
size <-  ifelse(grepl("10", resfile), "10", "5")

  tmp2 <- tidy_df(x, colLabels = rep(filename[l], length(x)), 
                 fill =  "FDR", annotate = NULL, alpha = 0.10) %>%
    mutate(fdr = nrejects) %>%
    select(method, casestudy, replicate, fdr)
  tmp3 <- tidy_df(x, colLabels = rep(filename[l], length(x)), 
                  fill =  "TNR", annotate = NULL, alpha = 0.10) %>%
    mutate(tnr = nrejects) %>%
  select(method, casestudy, replicate, tnr)

  if (type[l] != "null"){
    tmp1 <- tidy_df(x, colLabels = rep(filename[l], length(x)), 
                    fill =  "TPR", annotate = NULL, alpha = 0.10) %>%
      mutate(tpr = nrejects) %>%
    select(method, casestudy, replicate, tpr)

    tmp <- left_join(tmp1, tmp2, by = c("method", "casestudy", "replicate")) %>%
      left_join(tmp3, by = c("method", "casestudy", "replicate")) %>%
      mutate(inform = inform[l],
             type = type[l],
             size = size[l])
  }else{
    tmp <- left_join(tmp2, tmp3, by = c("method", "casestudy", "replicate")) %>%
      mutate(inform = inform[l],
             type = type[l],
             size = size[l])
  }

# take difference within replicate, then average differences across
# type and size and method

dftab <- tab %>%
  filter(method %in% cov.methods) %>%
  dplyr::mutate(id = paste(type, size, method, replicate, sep = "-"))

uninftab <- dftab %>% 
  filter(inform == "uninf") %>%
  select(id, fdr, tpr, tnr) %>%
  rename(fdr = "fdr_uninf",
         tnr = "tnr_uninf",
         tpr = "tpr_uninf")

inftab <- dftab %>%
  filter(inform == "inf") %>%
  select(-inform)

dftab <- left_join(inftab, uninftab, by = "id") %>%
  mutate(tpr_diff = tpr-tpr_uninf,
         fdr_diff = fdr-fdr_uninf,
         tnr_diff = tnr-tnr_uninf) %>%
  group_by(type, size, method) %>%
  summarize(tpr_se = sqrt(sd(tpr_diff)/n()),
            fdr_se = sqrt(sd(fdr_diff)/n()),
            tnr_se = sqrt(sd(tnr_diff)/n()),
            tpr_diff = mean(tpr_diff),
            fdr_diff = mean(fdr_diff),
            tnr_diff = mean(tnr_diff)) %>%
  mutate(method = factor(method, levels = rowOrder)) %>%
  mutate(fdr_diff = ifelse(type == "null", NA, fdr_diff),
         tpr_diff = ifelse(type == "null", NA, tpr_diff),
         fdr_se = ifelse(type == "null", NA, fdr_se),
         tpr_se = ifelse(type == "null", NA, tpr_se))

plot_fun <- function(var){

  plot  <- ggplot(dftab %>% filter(!is.na(get(var))), 
                  aes(x = interaction(type, size), 
                                        y = method)) + 
    geom_tile(aes(fill=get(var))) + 
    scale_fill_gradient2(paste0("Change\nin ", toupper(gsub("_diff", "", var))),
                         low = "red", midpoint = 0, mid = "white", high = "blue",
                         labels = scales::percent) +
    theme_bw() +
    xlab("Experiment") +
    ylab("Method") +
    facet_grid( ~ type + size, scales = "free", space = "free") +
    ggtitle(paste0("Impact of informative covariate on ", toupper(gsub("_diff", "", var)))) +
    theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1)) +
    geom_text(aes(label = scales::percent(get(var))),
            color = "black", size = 3)

  return(plot)
}

# arrange in multipanel figure?
plot_fun("tpr_diff")
ggsave(file.path(outdir, paste0("Figure_infCov_tpr_", org, ".pdf")), height = 5, width = 5)

plot_fun("fdr_diff")
ggsave(file.path(outdir, paste0("Figure_infCov_fpr_", org, ".pdf")), height = 5, width = 5)

plot_fun("tnr_diff")
ggsave(file.path(outdir, paste0("Figure_infCov_tnr_", org, ".pdf")), height = 5, width = 7)

}

>>>>

# not excluding any methods
Fig4All.rowOrder <- c("bonf", "bh", "ihw", "qvalue", "bl", "lfdr",
                  "fdrreg-e", "fdrreg-t", "ashq")
Fig4All <- plotMethodRanks(objects, colLabels = casestudy, alpha = alpha,
                        excludeMethods = NULL, rowOrder = Fig4All.rowOrder) +
        theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1),
              legend.position = c(0.98, 0.93), legend.justification = c(1, 1),
              legend.background = element_rect(fill = scales::alpha("white", 3/4), color = 'black'),
              legend.direction = "horizontal",
              legend.text = element_text(size = 7),
              legend.title = element_text(size = 9),
              legend.margin = margin(6, 10, 6, 10))

@@

print(xtable(tabS3), include.rownames=FALSE)

@@

pfdr <- plotMethodRanks(objs, 
                colLabels = c("sim", "sim"), 
                alpha = alpha, xlab = "Comparison",
                fill = "FDR",
                rowOrder = Fig4All.rowOrder, 
                annotate = "FDR", excludeMethods = NULL) +
          scale_fill_gradient2(high = "darkred", 
                         mid = "white", 
                         low = "#2171B5", 
                         midpoint = alpha) +
          labs(fill = "Mean FDR") +
          theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1),
              legend.justification = c(1, 0.5),
              legend.text = element_text(size = 7),
              legend.title = element_text(size = 8),
              legend.margin = margin(1, 1, 1, 1)) +
          ylab("") + xlab("") +  
          theme(plot.margin=unit(c(5.5, 5.5, 30, 5.5), "points"))

@@

ggdraw() +
  draw_plot(pfdr, 0.53, 0, 0.23, 1) +
  draw_plot(ptpr, 0.76, 0, 0.23, 1) +
  draw_plot(Fig4All, 0, 0, 0.52, 1) +
  draw_plot_label(c("A", "B"), c(0, 0.53), c(1, 1), size = 15) +
  draw_plot_label("Simulation", 0.69, 0.06, size =11, fontface = "plain")
ggsave(file.path(outdir, "Figure4.pdf"), width=9, height=5)

@@

```{r, fig.width = 6, fig.height = 4}
casestudy.tab <- mutate(casestudy.tab, prop_casestudy = mean_prop) %>%
  select(casestudy, method, prop_casestudy)
yeastsim.tab <- yeastsim.tab %>% 
  mutate(prop_yeastsim = mean_prop) %>% 
  filter(casestudy == "de5") %>%
  select(casestudy, method, prop_yeastsim)

@@

ggplot(rank.tab %>% filter(method != "bonf"), 
       aes(y = prop_casestudy, x = prop_yeastsim, group = prop_yeastsim, color=Method)) +
  geom_boxplot(aes(x = prop_yeastsim, y = prop_casestudy),
                   alpha = 0.3, position = position_dodge(width = 0),
                   width = 0.02) +
  scale_color_manual(values=col) +
  theme_bw() +
  xlab("Proportion of maximum rejections in yeast simulation (n=5s)") +  
  ylab("Proportion of maximum rejections in casestudies") +
  labs(shape = "Case Study") 
ggsave(file.path(outdir, "Figure_simVcasestudyRanks_scaled.pdf"), width=6, height=4)

@@

@@

Here we'll contrast the results of informative and uninformative covariates 
on the yeast and polyester simulation (DE sample size 5). We'll plot
differences in TPR and FDR due to informative covariate by alpha level.

```{r, fig.width = 10, fig.height = 4}
for (org in c("yeast", "polyester")){

  objects <- list.files( path, recursive=TRUE, pattern="rds", full.names=TRUE )
  resfile <- objects[grepl(org, objects) ] 
  resfile <- resfile[grepl("5", resfile) & !grepl("null", resfile)]

  # regexp to construct master data table separating case study datasets, methods
  # and covariates
  obj.names <- str_split(resfile, pattern = "/")
  casestudy <- unlist(lapply(obj.names, function(x) x[3] ))
  filename <- gsub(".rds", "", unlist(lapply(obj.names, function(x) x[4] )))
  dataset <- unlist(lapply(str_split(filename, pattern = "-"), function(x) x[[3]]))
  inform <-  ifelse(grepl("uninf", resfile), "uninf", "inf")
  type <-  ifelse(grepl("null", resfile), "null", "de")
  size <-  ifelse(grepl("10", resfile), "10", "5")
  aseq <- seq(0.01, 0.10, by = 0.01)

    tmp2 <- tidy_df(x, colLabels = rep(filename[l], length(x)), 
                    fill =  "FDR", annotate = NULL, 
                    alpha = aseq) %>%
      mutate(fdr = nrejects) %>%
      select(method, casestudy, replicate, fdr, alpha)
    tmp3 <- tidy_df(x, colLabels = rep(filename[l], length(x)), 
                    fill =  "TNR", annotate = NULL, 
                    alpha = aseq) %>%
      mutate(tnr = nrejects) %>%
      select(method, casestudy, replicate, tnr, alpha)

    if (type[l] != "null"){
      tmp1 <- tidy_df(x, colLabels = rep(filename[l], length(x)), 
                      fill =  "TPR", annotate = NULL, 
                      alpha = aseq) %>%
        mutate(tpr = nrejects) %>%
        select(method, casestudy, replicate, tpr, alpha)

      tmp <- left_join(tmp1, tmp2, by = c("method", "casestudy", "replicate", "alpha")) %>%
        left_join(tmp3, by = c("method", "casestudy", "replicate", "alpha")) %>%
        mutate(inform = inform[l],
               type = type[l],
               size = size[l])
    }else{
      tmp <- left_join(tmp2, tmp3, by = c("method", "casestudy", "replicate", "alpha")) %>%
        mutate(inform = inform[l],
               type = type[l],
               size = size[l])
    }

myspread <- function(df, key, value) {
    # quote key
    keyq <- rlang::enquo(key)
    # break value vector into quotes
    valueq <- rlang::enquo(value)
    s <- rlang::quos(!!valueq)
    df %>% gather(variable, value, !!!s) %>%
        unite(temp, !!keyq, variable) %>%
        spread(temp, value)
}

dftab <- tab %>%
  select(-casestudy) %>%
  myspread(inform, c(tpr, fdr, tnr))

dftab <- dftab %>%
  mutate(tpr_diff = inf_tpr - uninf_tpr,
         fdr_diff = inf_fdr - uninf_fdr,
         tnr_diff = inf_tnr - uninf_tnr) %>%
  group_by(type, size, method, alpha) %>%
  summarize(tpr_se = sd(tpr_diff)/n(),
            fdr_se = sd(fdr_diff)/n(),
            tnr_se = sd(tnr_diff)/n(),
            tpr_diff = mean(tpr_diff),
            fdr_diff = mean(fdr_diff),
            tnr_diff = mean(tnr_diff))

col <- as.character(candycols$col)
names(col) <- as.character(candycols$Method)
lty <- as.character(candycols$lty)
names(lty) <- as.character(candycols$Method)

lineplot_fdr <- ggplot(dftab,
                       aes(x = alpha, y = fdr_diff, color = method, linetype = method)) +
    geom_hline(yintercept = 0, lty = 2, color = "blue", alpha = 1/2) + 
    geom_line(alpha = 0.85) +
    geom_errorbar(width=.003, alpha = 0.5, aes(ymin = fdr_diff - fdr_se, 
                                ymax = fdr_diff + fdr_se)) +
    scale_linetype_manual(values = lty) + 
    scale_color_manual(values = col) +
    scale_x_continuous("alpha", breaks = seq(0, 1, .01)) + 
    scale_y_continuous(expression(paste("Mean ", Delta, "FDR (informative-uninformative)")), 
                       breaks = seq(-1, 1, .005), labels = scales::percent) + 
    ggtitle("FDR difference with informative covariate") +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 11, hjust = 0.8))

lineplot_tpr <- ggplot(dftab, aes(x = alpha, y = tpr_diff, color = method, linetype = method)) +
    geom_hline(yintercept = 0, lty = 2, color = "blue", alpha = 1/2) + 
    geom_errorbar(width=.003, alpha = 0.5, aes(ymin = tpr_diff - tpr_se, 
                                ymax = tpr_diff + tpr_se)) +
    geom_line(alpha = 0.85) +
    scale_linetype_manual(values = lty) + 
    scale_color_manual(values = col) +
    scale_x_continuous("alpha", breaks = seq(0, 1, .01)) + 
    scale_y_continuous(expression(paste("Mean ", Delta, "TPR (informative-uninformative)")), 
                       labels = scales::percent) + 
    ggtitle("TPR difference with informative covariate") +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 11))

  gp <- plot_grid(lineplot_fdr + guides(color = FALSE, linetype = FALSE),
                  lineplot_tpr + guides(color = FALSE, linetype = FALSE),
                  labels = LETTERS[1:2], nrow = 1)
  gp <- plot_grid(gp, get_legend(lineplot_fdr), rel_widths = c(1, 1/8))
  gp
  ggsave(file.path(outdir, paste0("Figure_infCov_", org, ".pdf")), height = 3.5, width = 8)
}
```

## Case study rankings

This is a figure similar to Figure 4, except that we 
include all case studies in a single plot.

@@

## Informativeness of covariates in case studies

@@
